Supplementary Figures relative to feature selection

### 2020-07-02 supplementary_figures/supp5_dr.Rmd
added supp figure on dimensionality-nbClusts

```{r, fig.width=8, fig.height=8.5}
library(viridis)
res <- readRDS("../data/clust_endSummary.rds")
res2 <- res[which(res$clust=="clust.seurat" & res$k==20 & res$dims>2 & res$resolution > 0.05 & res$resolution <= 1),]
res2 <- res2[which(res2$dr=="seurat.pca" & res2$dataset!="Kumar"),]
res3 <- aggregate(res2[,"ARI",drop=FALSE], by=res2[,c("dataset","dims","resolution")], FUN=mean)
ll <- lapply(split(res3, res3$dataset), FUN=function(x){
  ggplot(x, aes(factor(dims), factor(resolution), fill=ARI)) + stat_bin2d() + 
    scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
for(i in names(ll)) ll[[i]] <- ll[[i]] + ggtitle(i)
plot_grid(plotlist = ll, nrow=3)
```

### Supplementary Figure `r getFigNb()`
Adjusted Rand Index of clustering depending on the resolution and number of dimensions used. Based on sctransform and seurat PCA.

>>>>

```{r, fig.width=8, fig.height=8.5}
res3 <- aggregate(res2[,"ARI",drop=FALSE], by=res2[,c("dataset","dims","resolution")], FUN=mean)
ll <- lapply(split(res3, res3$dataset), FUN=function(x){
  ggplot(x, aes(factor(dims), factor(resolution), fill=ARI)) + stat_bin2d() + 
    scale_fill_viridis() + ylab("Resolution") + xlab("Number of dimensions") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
for(i in names(ll)) ll[[i]] <- ll[[i]] + ggtitle(i)
plot_grid(plotlist = ll, nrow=3)
```

### Supplementary Figure `r getFigNb()`

Adjusted Rand Index of clustering depending on the resolution and number of dimensions used. Based on sctransform
and seurat PCA.

```{r, fig.width=7.5, fig.height=8.5}
cl <- readRDS("../data/results_dimensionality.rds")$evaluation$clustering
cl$delta.nbClust <- cl$n_clus-cl$true.nbClusts

cl$dims <- gsub("maxLikGlobal$","maxLikGlobal(k=20)",cl$dims)
cl$dims <- gsub("maxLikGlobal10$","maxLikGlobal(k=10)",cl$dims)
cl <- cl[cl$norm=="norm.seurat" & !(cl$dims %in% c("10","30","essLocal.b")),]

ggplot(cl, aes(x=dims, y=delta.nbClust, fill=dims)) + geom_violin() + 
  facet_wrap(~dataset, scales = "free_x", ncol = 2) + coord_flip() + 
  stat_summary(size=0.25, fun.data = mean_se, na.rm = TRUE) + 
  geom_hline(yintercept = 0, linetype="dashed") + xlab("") +
  theme(legend.position="none", text=element_text(size=10)) + 
  ylab("Deviation from true number of clusters")
```

### Supplementary Figure `r getFigNb()`

Deviation from the true number of clusters using different number of principal components (based the indicated dimensionality estimates) of the same Seurat-based PCA. Default pipeline parameters were used for the other steps, and the distributions represent the different resolutions of Seurat clustering. Across datasets, MCVR and maxLikGlobal appear to depart less from the true number of clusters.

### 2020-07-02 supplementary_figures/supp_overall.Rmd
added supp figure on dimensionality-nbClusts

>>>>

# checking for interactions:
# mod <- lm(ARI~resolution*dataset+doubletmethod*sel*filt*norm*clustmethod*dims, data=cl)
# co <- as.data.frame(coef(summary(mod)))
# coi <- co[grep(":",row.names(co)),]
# coi <- coi[grep("dataset", row.names(coi), invert=TRUE),]
# colnames(coi) <- c("Estimate","SE","t","p.value")
# coi <- coi[order(coi$p.value),]
